---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(ggplot2)
library(odin)
library(tidyr)
library(dplyr)
library(pkgbuild)
library(rmarkdown)
library(demodelr)
library(plotly)
library(ggthemes)
library(extrafont)
library(ggpattern)
library(here)

path <- here::here("Script", "DeuxAgeDeuxResistanceOdin.R")
code <- paste(readLines(path, warn = FALSE), collapse = "\n")
gen <- odin::odin(code)

```


##ArticleVaron 2000 Groupe Erythromicine

#Code to generate a function that sets the transmissibility parameters (Beta and f) in order to achieve steady state at the initial conditions.
```{r optim global Vi et fi}

OptimViFi <- function(x,y) {
    mod <- gen$new(US_0=c((1000*(1-(0.052)))*0.53),
               UCm1_0=c((1000*(1-(0.052)))*0.47*0.47),
               UCm2_0=c((1000*(1-(0.052)))*0.47*0.53),
               
               ES_0=c((1000*0.052)*0.53),
               ECm1_0=c((1000*0.052)*0.47*0.47),
               ECm2_0=c((1000*0.052)*0.47*0.53),
               
               f=x[1],
               a1=0,a2=1,
               
               V=c(x[2]),
               Beta=matrix(c(1),nrow = 1, ncol = 1 ,byrow = TRUE),
               Phi=c(0.07/31),
               Mu=c(0), 
               mu0=0,
               Lambda=c(1/43),
               gamma=1/(8),
               dose1= y[1], #1000mg,q8h MIC=0.06
               dose2=y[2], #1000mg,q8h MIC=8
               pm1m2=0,
               theta=0.5,
               N_age=1)
        
    t <- seq(0, 365*5,0.1)
    y_odin <- mod$run(t)
    out_odin <- as.data.frame(y_odin)
    
    out_odin=out_odin[c(nrow(out_odin)),]
    
    out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `S[1]`=`US[1]`+`ES[1]`,
    `Cm1[1]`=`UCm1[1]`+`ECm1[1]`,
    `Cm2[1]`=`UCm2[1]`+`ECm2[1]`,
    `Totcarrier[1]`=`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    `Tot[1]`=`US[1]`+`ES[1]`+`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    .keep = "none"
  )
    out_odin = out_odin %>%
    mutate(
    `t`=`t`,
    `Cm1[1]`=`Cm1[1]`/`Totcarrier[1]`,
    `Cm2[1]`=`Cm2[1]`/`Totcarrier[1]`,
    `Totcarrier[1]`=`Totcarrier[1]`/`Tot[1]`,
    .keep = "none"
  )
    
    
    f=out_odin
    p1=as.numeric(f[4])
    r1=as.numeric(f[3])
    
    #cat(x[1]," :",p1,x[2]," :",r1)
    
    return(abs(0.48-p1)**2+abs(0.44-r1)**2)
}

```

#Code to generate a function that calculates the value of the antibiotic's effect to reproduce the observations
```{r optim Dose pour obtenir les variations}

OptimDose <- function(x) {
  
  Optimi<-optim(par=c(0.72,0.01),OptimViFi,y=c(x[1],x[2]),control = list(maxit = 20000))
  
  fi<-Optim$par[1]
  Vi<-Optimi$par[2]
  
    mod <- gen$new(US_0=c(0),
               UCm1_0=c(0),
               UCm2_0=c(0),
               
               ES_0=c(86*0.53),
               ECm1_0=c(86*0.47*0.47),
               ECm2_0=c(86*0.47*0.53),

               
               f=fi,
               #f=0.82020079,
               a1=0,a2=1,
               
               V=Vi,
               #V=0.01926239,
               Beta=matrix(c(1),nrow = 1, ncol = 1 ,byrow = TRUE),
               Phi=c(0),
               Mu=c(0),  
               mu0=0,
               Lambda=c(1/43), #décolonisation naturelle 
               gamma=1/8,
               dose1= x[1], #1000mg,q8h MIC<=0.063
               dose2=x[2], #1000mg,q8h MIC>=0.125
               pm1m2=0,
               theta=0.5,
               N_age=1)
        
    t <- seq(0,10,1)
    y_odin <- mod$run(t)
    out_odin <- as.data.frame(y_odin)
    
    out_odin=out_odin[c(nrow(out_odin)),]
    
    out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `S[1]`=`US[1]`+`ES[1]`,
    `Cm1[1]`=`UCm1[1]`+`ECm1[1]`,
    `Cm2[1]`=`UCm2[1]`+`ECm2[1]`,
    `Totcarrier[1]`=`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    `Tot[1]`=`US[1]`+`ES[1]`+`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    .keep = "none"
  )
    out_odin = out_odin %>%
    mutate(
    `t`=`t`,
    `Cm1[1]`=`Cm1[1]`/`Totcarrier[1]`,
    `Cm2[1]`=`Cm2[1]`/`Totcarrier[1]`,
    `Totcarrier[1]`=`Totcarrier[1]`/`Tot[1]`,
    .keep = "none"
  )
  
    f=out_odin
    p1=as.numeric(f[4])
    r1=as.numeric(f[3])
    
    #cat(x[1]," ",x[2]," ",fi," ",Vi," :",r1," ",p1,"\n")
    
    return(abs(0.91-r1)**2+abs(0.25-p1)**2)
}

res_AntibioEffect <- data.frame()


for (i in 1:10) {

  x0 <- c(runif(2, min = 0,  max = 1))

  fit <- optim(
    par = x0, fn = OptimDose, method = "L-BFGS-B",
    lower = c(0, 0), upper = c(1, 1)
  )

  DoseEffectS <- fit$par[1]
  DoseEffectR <- fit$par[2]

  res_AntibioEffect <- rbind(
    res_AntibioEffect,
    data.frame(
      seed = i,
      DoseEffectS = DoseEffectS,
      DoseEffectR = DoseEffectR
    )
  )
}

res_AntibioEffect
  
mean_DoseEffectS <- mean(res_AntibioEffect$DoseEffectS, na.rm = TRUE)
mean_DoseEffectR <- mean(res_AntibioEffect$DoseEffectR, na.rm = TRUE)

cat(mean_DoseEffectS," ",mean_DoseEffectR)


```

#Code to generate the evolution of carriage with the fitted parameters
```{r setup, include=FALSE}

mean_DoseEffectS<-1
mean_DoseEffectR<-0.03449561

Optim=optim(par=c(0.72,0.01),OptimViFi,y=c(mean_DoseEffectS,mean_DoseEffectR),control = list(maxit = 20000))
f_f<-Optim$par[1] #0.9345706
V_f<-Optim$par[2] #0.07551792
cat(f_f," ",V_f )
# 5ans 0.9352253   0.07550239


mod <- gen$new(US_0=c(0),
               UCm1_0=c(0),
               UCm2_0=c(0),
               
               ES_0=c(86*0.53),
               ECm1_0=c(86*0.47*0.47),
               ECm2_0=c(86*0.47*0.53),
               
               f=f_f              ,
               a1=0,a2=1,
               
               V=c(V_f),
               Beta=matrix(c(1),nrow = 1, ncol = 1 ,byrow = TRUE),
               
               Phi=c(0),
               Mu=c(0),  #c((0.76*10**(-3))/365,(0.1*10**(-3))/365,(2.16*10**(-3))/365,(50*10**(-3))/365),
               mu0=0,
               Lambda=c(1/43), #décolonisation naturelle 
               gamma=1/8,
               dose1= mean_DoseEffectS       , #1000mg,q8h MIC<=0.063
               dose2=mean_DoseEffectR    , #1000mg,q8h MIC>=0.125
               pm1m2=0,
               theta=0.5,
               N_age=1)



```

#Code to generate Supplementary Figure S11
```{r ggplot distribution des CMI}
t <- seq(0,10,0.1)
y_odin <- mod$run(t)
out_odin <- as.data.frame(y_odin)
out_odin=out_odin[c(1,nrow(out_odin)),]

out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `Cm1[1]`=`UCm1[1]`+`ECm1[1]`,
    `Cm2[1]`=`UCm2[1]`+`ECm2[1]`,
    `Totcarrier[1]`=`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    `Tot[1]`=`US[1]`+`ES[1]`+`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    .keep = "none"
  )

out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `Cm1_Simulation`=`Cm1[1]`/`Totcarrier[1]`,
    `Cm2_Simulation`=`Cm2[1]`/`Totcarrier[1]`,
    `Totcarrier_Simulation`=`Totcarrier[1]`/`Tot[1]`,
    .keep = "none"
  )
out_odin[1,1]=1

df2<-data.frame(`t`=numeric(), `Cm1_Observation`=numeric(), `Cm2_Observation`=numeric(),`Totcarrier_Observation`=numeric() )
df2[1,]<-c(1,0.47,0.53,0.47)
df2[2,]<-c(10,0.09,0.91,0.25)
df_merged=merge(out_odin,df2, by="t")


out_long= df_merged %>% pivot_longer(
  cols = `Cm1_Simulation`:`Totcarrier_Observation`,
  names_to = c("Compartment","Datas"),
  names_pattern = "([A-Za-z0-9]+)_(.+)",
  values_to = "count"
)


# Ouvrir un périphérique graphique pour sauvegarder le plot en tant qu'image PNG
png(filename = here::here("Figures", "FigureS11Macrolides.png"), width =1000, height = 800)

ggplot(out_long,aes(x=Compartment,y=count, fill=Compartment,alpha = factor(t),pattern = Datas))+
  geom_col_pattern( position = position_dodge(), color = "black")+
   scale_fill_manual(
    name = "Données",
    values = c("Cm1" = "#32CD32",  
               "Cm2" = "#FF6347", 
               "Totcarrier" = "#1E90FF"),
    guide = guide_legend(override.aes = list(pattern = "none")) 
  ) +
  scale_alpha_manual(
    values = c(0.4, 1),  # Plus clair pour t=0, plus opaque pour t=365
    name = "Time",
    labels = c("Baseline", "8-days"),
    guide = guide_legend(override.aes = list( pattern = c("none", "none")))
  ) +
  scale_pattern_manual(
    values = c("Simulation" = "stripe", "Observation" = "none"),  # Ajustez les motifs selon votre colonne 'Datas'
    name = "Datas"
  ) +
  geom_errorbar(data = dplyr::filter(out_long,t==1& Datas=="Observation"), aes(ymin=count-1.96*sqrt((count*(1-count))/86), ymax=count+1.96*sqrt((count*(1-count))/86)), position=position_nudge(x=-0.33),width = 0.2)+
   geom_errorbar(data = dplyr::filter(out_long,t==10& Datas=="Observation"), aes(ymin=count-1.96*sqrt((count*(1-count))/86), ymax=count+1.96*sqrt((count*(1-count))/86)), position=position_nudge(x=0.1),width = 0.2)+
  geom_text(aes(label=round(count,2)),position = position_dodge(0.9),vjust=-2,show.legend = FALSE,size=7,face = "bold")+
  xlab("Outcome")+ylab("Proportion")+
  scale_x_discrete(labels = c("MSSP", "MRSP", "TotCarrier"))+
  theme_clean()+
  theme(legend.background = element_rect(fill = "white", colour = "black"),legend.key.width =unit(1.4, "cm"),
        legend.title=element_text(size = 22),legend.text=element_text(size = 20),
        legend.direction = "vertical",legend.box = "horizontal", legend.box.just = "center",legend.position = "bottom",
        axis.text = element_text(size =18),axis.title = element_text(size = 20),
        strip.text = element_text(size = 25, face = "bold",hjust = 0.5),strip.placement = "outside",
        panel.border = element_blank() ,plot.background = element_blank())

# Fermer le périphérique graphique
dev.off()


```



##Article Lewnard et al. 2018 Groupe Amoxicilline Clavulanate

#Code to generate a function that sets the transmissibility parameters (Beta and f) in order to achieve steady state at the initial conditions.
```{r optim global Vi et fi}

OptimFiVi <- function(x,y) {
    mod <- gen$new(US_0=c((1000*(1-(0.02258065)))*0.36),
               UCm1_0=c((1000*(1-(0.02258065)))*0.64*0.81),
               UCm2_0=c((1000*(1-(0.02258065)))*0.64*0.19),
               
               ES_0=c((1000*0.02258065)*0.36),
               ECm1_0=c((1000*0.02258065)*0.64*0.81),
               ECm2_0=c((1000*0.02258065)*0.64*0.19),
               
               f=x[1],
               a1=0,a2=1,
               
               V=c(x[2]),
               Beta=matrix(c(1),nrow = 1, ncol = 1 ,byrow = TRUE),

               Phi=c(0.2*0.5/31), #*0.5 car 2 fois moins d'exposition en Finlande que en Franve
               Mu=c(0),  
               mu0=0,
               Lambda=c(1/43),
               gamma=1/7,
               dose1= y[1], #1000mg,q8h MIC=0.06
               dose2=y[2], #1000mg,q8h MIC=8
               pm1m2=0,
               theta=0.5,
               N_age=1)
        
    t <- seq(0, 365*5,0.1)
    y_odin <- mod$run(t)
    out_odin <- as.data.frame(y_odin)
    
    out_odin=out_odin[c(nrow(out_odin)),]
    
    out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `S[1]`=`US[1]`+`ES[1]`,
    `Cm1[1]`=`UCm1[1]`+`ECm1[1]`,
    `Cm2[1]`=`UCm2[1]`+`ECm2[1]`,
    `Totcarrier[1]`=`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    `Tot[1]`=`US[1]`+`ES[1]`+`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    .keep = "none"
  )
    out_odin = out_odin %>%
    mutate(
    `t`=`t`,
    `Cm1[1]`=`Cm1[1]`/`Totcarrier[1]`,
    `Cm2[1]`=`Cm2[1]`/`Totcarrier[1]`,
    `Totcarrier[1]`=`Totcarrier[1]`/`Tot[1]`,
    .keep = "none"
  )
    
    
    f=out_odin
    p1=as.numeric(f[4])
    r1=as.numeric(f[3])
    
    #cat(x[1]," :",p1,x[2]," :",r1)
    
    return(abs(0.64-p1)**2+abs(0.19-r1)**2)
}


```

#Code to generate a function that calculates the value of the antibiotic's effect to reproduce the observations
```{r optim Dose pour obtenir les variations}

OptimDose <- function(x) {
  
    fi<-optim(par=c(0.72,0.01),OptimFiVi,y=c(x[1],x[2]),control = list(maxit = 20000))$par[1]
    Vi<-optim(par=c(0.72,0.01),OptimFiVi,y=c(x[1],x[2]),control = list(maxit = 20000))$par[2]
    
    mod <- gen$new(US_0=c(0),
               UCm1_0=c(0),
               UCm2_0=c(0),
               
               ES_0=c(146*0.36),
               ECm1_0=c(146*0.64*0.81),
               ECm2_0=c(146*0.64*0.19),

               
               f=fi,
               a1=0,a2=1,
               
               V=Vi,
               Beta=matrix(c(1),nrow = 1, ncol = 1 ,byrow = TRUE),
               Phi=c(0),
               Mu=c(0),  
               mu0=0,
               Lambda=c(1/43), #décolonisation naturelle 
               gamma=1/7,
               dose1= x[1], #1000mg,q8h MIC<=0.063
               dose2=x[2], #1000mg,q8h MIC>=0.125
               pm1m2=0,
               theta=0.5,
               N_age=1)
        
    t <- seq(0,8,1)
    y_odin <- mod$run(t)
    out_odin <- as.data.frame(y_odin)
    
    out_odin=out_odin[c(nrow(out_odin)),]
    
    out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `S[1]`=`US[1]`+`ES[1]`,
    `Cm1[1]`=`UCm1[1]`+`ECm1[1]`,
    `Cm2[1]`=`UCm2[1]`+`ECm2[1]`,
    `Totcarrier[1]`=`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    `Tot[1]`=`US[1]`+`ES[1]`+`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    .keep = "none"
  )
    out_odin = out_odin %>%
    mutate(
    `t`=`t`,
    `Cm1[1]`=`Cm1[1]`/`Totcarrier[1]`,
    `Cm2[1]`=`Cm2[1]`/`Totcarrier[1]`,
    `Totcarrier[1]`=`Totcarrier[1]`/`Tot[1]`,
    .keep = "none"
  )
  
    f=out_odin
    p1=as.numeric(f[4])
    r1=as.numeric(f[3])
    
    #cat(x[1],x[2]," :",r1," ",p1,"\n")
    
    return(abs(0.67-r1)**2+abs(0.13-p1)**2)
}


res_AntibioEffect <- data.frame()


for (i in 1:10) {

  x0 <- c(runif(2, min = 0,  max = 1.0))

  fit <- optim(
    par = x0, fn = OptimDose, method = "L-BFGS-B",
    lower = c(0, 0), upper = c(1, 1)
  )

  DoseEffectS <- fit$par[1]
  DoseEffectR <- fit$par[2]

  res_AntibioEffect <- rbind(
    res_AntibioEffect,
    data.frame(
      seed = i,
      DoseEffectS = DoseEffectS,
      DoseEffectR = DoseEffectR
    )
  )
}

res_AntibioEffect
  
mean_DoseEffectS <- mean(res_AntibioEffect$DoseEffectS, na.rm = TRUE)
mean_DoseEffectR <- mean(res_AntibioEffect$DoseEffectR, na.rm = TRUE)

cat(mean_DoseEffectS," ",mean_DoseEffectR)



```

#Code to generate the evolution of carriage with the fitted parameters
```{r run the model with fitted parameters}

mean_DoseEffectS<-1
mean_DoseEffectR<-0.08799847

Optim=optim(par=c(0.72,0.01),OptimFiVi,y=c(mean_DoseEffectS,mean_DoseEffectR),control = list(maxit = 20000))
f_f<-Optim$par[1] #0.9345706
V_f<-Optim$par[2] #0.07551792
cat(f_f," ",V_f )
# 5ans 0.9352253   0.07550239


mod <- gen$new(US_0=c(0),
               UCm1_0=c(0),
               UCm2_0=c(0),
               
               ES_0=c(146*0.36),
               ECm1_0=c(146*0.64*0.81),
               ECm2_0=c(146*0.64*0.19),
               
               f=f_f     ,
               a1=0,a2=1,
               
               V=c(V_f),
               Beta=matrix(c(1),nrow = 1, ncol = 1 ,byrow = TRUE),
               
               Phi=c(0),
               Mu=c(0),  #c((0.76*10**(-3))/365,(0.1*10**(-3))/365,(2.16*10**(-3))/365,(50*10**(-3))/365),
               mu0=0,
               Lambda=c(1/43), #décolonisation naturelle 
               gamma=1/7,
               dose1= mean_DoseEffectS , #1000mg,q8h MIC<=0.063
               dose2=mean_DoseEffectR, #1000mg,q8h MIC>=0.125
               pm1m2=0,
               theta=0.5,
               N_age=1)



```

#Code to generate Supplementary Figure S10
```{r ggplot distribution des CMI}

t <- seq(0,8,0.1)
y_odin <- mod$run(t)
out_odin <- as.data.frame(y_odin)
out_odin=out_odin[c(1,nrow(out_odin)),]

out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `Cm1[1]`=`UCm1[1]`+`ECm1[1]`,
    `Cm2[1]`=`UCm2[1]`+`ECm2[1]`,
    `Totcarrier[1]`=`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    `Tot[1]`=`US[1]`+`ES[1]`+`UCm1[1]`+`ECm1[1]`+`UCm2[1]`+`ECm2[1]`,
    .keep = "none"
  )

out_odin = out_odin %>%
  mutate(
    `t`=`t`,
    `Cm1_Simulation`=`Cm1[1]`/`Totcarrier[1]`,
    `Cm2_Simulation`=`Cm2[1]`/`Totcarrier[1]`,
    `Totcarrier_Simulation`=`Totcarrier[1]`/`Tot[1]`,
    .keep = "none"
  )
out_odin[1,1]=1

df2<-data.frame(`t`=numeric(), `Cm1_Observation`=numeric(), `Cm2_Observation`=numeric(),`Totcarrier_Observation`=numeric() )
df2[1,]<-c(1,0.81,0.19,0.64)
df2[2,]<-c(8,0.33,0.67,0.13)
df_merged=merge(out_odin,df2, by="t")


out_long= df_merged %>% pivot_longer(
  cols = `Cm1_Simulation`:`Totcarrier_Observation`,
  names_to = c("Compartment","Datas"),
  names_pattern = "([A-Za-z0-9]+)_(.+)",
  values_to = "count"
)


# Ouvrir un périphérique graphique pour sauvegarder le plot en tant qu'image PNG
png(filename = here::here("Figures", "FigureS10Amox.png"), width =1000, height = 800)

ggplot(out_long,aes(x=Compartment,y=count, fill=Compartment,alpha = factor(t),pattern = Datas))+
  geom_col_pattern( position = position_dodge(), color = "black")+
   scale_fill_manual(
    name = "Données",
    values = c("Cm1" = "#32CD32",  
               "Cm2" = "#FF6347", 
               "Totcarrier" = "#1E90FF"),
    guide = guide_legend(override.aes = list(pattern = "none")) 
  ) +
  scale_alpha_manual(
    values = c(0.4, 1),  # Plus clair pour t=0, plus opaque pour t=365
    name = "Time",
    labels = c("Baseline", "8-days"),
    guide = guide_legend(override.aes = list( pattern = c("none", "none")))
  ) +
  scale_pattern_manual(
    values = c("Simulation" = "stripe", "Observation" = "none"),  # Ajustez les motifs selon votre colonne 'Datas'
    name = "Datas"
  ) +
  geom_errorbar(data = dplyr::filter(out_long,t==1 & Datas=="Observation" ), aes(ymin=count-1.96*sqrt((count*(1-count))/86), ymax=count+1.96*sqrt((count*(1-count))/86)), position=position_nudge(x=-0.33),width = 0.2)+
  
   geom_errorbar(data = dplyr::filter(out_long,t==8 & Datas=="Observation"), aes(ymin=count-1.96*sqrt((count*(1-count))/86), ymax=count+1.96*sqrt((count*(1-count))/86)), position=position_nudge(x=0.1),width = 0.2)+
  
  geom_text(aes(label=round(count,2)),position = position_dodge(0.9),vjust=-2,show.legend = FALSE,size=7,face = "bold")+
  xlab("Outcome")+ylab("Proportion")+
  scale_x_discrete(labels = c("PSSP", "PNSP", "TotCarrier"))+
  theme_clean()+
  theme(legend.background = element_rect(fill = "white", colour = "black"),legend.key.width =unit(1.4, "cm"),
        legend.title=element_text(size = 22),legend.text=element_text(size = 20),
        legend.direction = "vertical",legend.box = "horizontal", legend.box.just = "center",legend.position = "bottom",
        axis.text = element_text(size =18),axis.title = element_text(size = 20),
        strip.text = element_text(size = 25, face = "bold",hjust = 0.5),strip.placement = "outside",
        panel.border = element_blank() ,plot.background = element_blank())

# Fermer le périphérique graphique
dev.off()





```




